### 2020-04-03 scache/jpdc/tex/model.tex
update

The FRQ model calculates the execution time of each phase of the job with these five parameters.
% As shown in Figure \ref{fig:model_basic}
The total execution time of a job is the sum of the map phase time and reduce phase time:
% \(T_{Job}=T_{Map}+T_{Reduce}\).
\begin{equation}
\label{equation_Tjob}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Reduce}
\end{aligned}
\end{equation}

@@

{\color{black}
\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and (\(K \times T_{P\_Shuffle}\)) represents the computing overhead.
\(T_{P\_Shuffle}\) represents the overlap time between the shuffle phase and the reduce phase as shown in Figure \ref{fig:model_basic}. \(T_{Shuffle}\) represents the total time of the shuffle phase. 
% The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks. This relationship will be shown in the following Subsection \ref{model_analysis}.  
\(K\) is an empirical value which represents the overhead caused by shuffle waiting. 
Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation needs to wait for the transfer results. This waiting causes the overhead.

>>>>

The FRQ model calculates the execution time of each phase of the job with these five parameters.
% As shown in Figure \ref{fig:model_basic}
The total execution time of a job is the sum of the map phase time and reduce phase time:
% \(T_{Job}=T_{Map}+T_{Reduce}\).
\begin{equation}
\label{equation_Tjob}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Reduce} + \edited{T_{Penalty}}
\end{aligned}
\end{equation}

@@

{\color{black}
\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and (\(K \times T_{P\_Shuffle}\)) represents the computing overhead.
\(T_{P\_Shuffle}\) represents the overlap time between the shuffle phase and the reduce phase as shown in Figure \ref{fig:model_basic}. \(T_{Shuffle}\) represents the total time of the shuffle phase. 
% The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks. This relationship will be shown in the following Subsection \ref{model_analysis}.  
\(K\) is an empirical value which represents the overhead caused by shuffle waiting. 
Because the computation of the reduce phase relies on the \edited{results of data transferring} of the shuffle phase, a portion of the computation needs to wait for the \edited{results of transferring}. This waiting causes the overhead.
